### 2017-10-01 TF-vldb2018/sec-expt.tex

%\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\ni (2) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
%Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.

>>>>

\ni (2) {\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\ni (3) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
%Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.

%\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.

### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
 redundant computations are avoid.

@@

\sstab{(i) Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
In this case, no computation is needed for maintaining partial relations for \affballsx at all,
\ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
Only a capacity check and an inner ball check in the combination procedure are needed (to see in Section~\ref{subsubsec-combine}).

>>>>

%In practice, the number of balls with type code ($0,\ldots,0$) is much larger than that of balls match with some pattern fragments, which is further larger than the number of \affballsx. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$), redundant computations are avoid.

@@

\sstab{(i) Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
In this case, no computation is needed for maintaining partial relations for \affballsx at all,
\ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
Only a capacity check and an inner ball check in the combination procedure are needed (to be seen immediately).
